Kernel Phase and Coronagraphy with Automatic Differentiation

### 2020-11-18 ms.tex

Although it is inefficient to calculate this full Jacobian with respect to a densely-pixelized basis for the wavefront in the pupil plane, we do so here for completeness. In practical cases, aberrations are typically dominated by low-order modes and we could consider the Jacobian only with respect to (for example) some much smaller number of Zernike modes. Reducing the input dimensionality like this would have significant advantages in memory usage for forwards-mode autodiff.

In Figure~\ref{kernel_jacobian} we display the results of our Jacobian calculation for a set of highlighted pupil samples and illustrating the influence of phase in the $u,v$ plane.

The results are similar to Figure~1 of \citet{martinache10}, consisting of the sums of translated positive and negative copies of the pupil aperture. Phase offsets outside the support of the pupil have identically zero derivative in the $u,v$ plane as expected. There is a greater magnitude in the derivative at longer baselines compared to the flat maps in \citet{martinache10} because we are rolling together the phase transfer $\mathbf{A}$ matrix and the redundancy matrix $\mathbf{R}$, and short baselines are much more redundant than long ones.

>>>>

Although it is inefficient to calculate this full Jacobian with respect to a densely-pixelized basis for the wavefront in the pupil plane, we do so here for completeness. In practical cases, aberrations are typically dominated by low-order modes and we could consider the Jacobian only with respect to (for example) some much smaller number of Zernike modes, or pixels in the $u,v$ plane. Reducing the input dimensionality like this would have significant advantages in memory usage for forwards-mode autodiff.

In Figure~\ref{kernel_jacobian} we display the results of our Jacobian calculation for a set of highlighted pupil samples and illustrating the influence of phase in the $u,v$ plane. 
The results are similar to Figure~1 of \citet{martinache10}, consisting of the sums of translated positive and negative copies of the pupil aperture. Phase offsets outside the support of the pupil have identically zero derivative in the $u,v$ plane as expected. There is a greater magnitude in the derivative at longer baselines compared to the flat maps in \citet{martinache10} because we are rolling together the phase transfer $\mathbf{A}$ matrix and the redundancy matrix $\mathbf{R}$, and short baselines are much more redundant than long ones.
